GLMM

### 2023-09-06 Code/GLMM.Rmd
Now includes 2023 data

---
title: "Random_Effects"
author: "Owen Fiore"
date: "2023-05-31"
output: pdf_document
---

@@

The code below loads in the 4 datasets from the csv file.
```{r}
#1
times <- read.csv("../Data/ThesisData.csv")
colnames(times) <- c("Year", "Type", "Time", "RxnTime", "Gender", "Batch")
men_finals <- subset(times, Type == "F" & Gender == "M" & Time != 'DQ')
men_pooled <- subset(times, (Type == "F" | Type == "S") & 
                       Gender == "M" & Time != 'DQ')
men_old_finals <- subset(times, Type == "F" & Gender == "M" & 
                           Time != 'DQ' & Year < 2022)
men_old_pooled <- subset(times, (Type == "F" | Type == "S") & 
                           Gender == "M" & Time != 'DQ' & Year < 2022)
```

@@

@@

This creates the models with a year effect and batch effect.
```{r}
#5
library(lme4)
men_old_finals_two_effect_gamma_log <- glmer(RxnTime ~ (1 | Year) + (1 | Batch), 
                                   data = men_old_finals, family = Gamma(link = "log"))
men_finals_two_effect_gamma_log<- glmer(RxnTime ~ (1 | Year) + (1 | Batch), 
                              data = men_finals, family = Gamma(link = "log"))
men_old_pooled_two_effect_gamma_log <- glmer(RxnTime ~ (1 | Year) + (1 | Batch), 
                                   data = men_old_pooled, family = Gamma(link = "log"))
men_pooled_two_effect_gamma_log <- glmer(RxnTime ~ (1 | Year) + (1 | Batch), 
                               data = men_pooled, family = Gamma(link = "log"))
```

@@

This next chunk of code runs the simulation code for each dataset comparing the
two effect model to the base model
```{r}
#7
sim_two_effect_time(men_old_finals_two_effect_gamma_log, men_old_finals_one_gamma_log, 0.1)
sim_two_effect_time(men_finals_two_effect_gamma_log, men_finals_one_gamma_log, 0.1)
sim_two_effect_time(men_old_pooled_two_effect_gamma_log, men_old_pooled_one_gamma_log, 0.1)
sim_two_effect_time(men_pooled_two_effect_gamma_log, men_pooled_one_gamma_log, 0.1)
```
```{r}
sim_two_effect_time(men_old_finals_two_effect_gamma_log, men_old_finals_one_gamma_log, 0.08)
sim_two_effect_time(men_finals_two_effect_gamma_log, men_finals_one_gamma_log, 0.08)
sim_two_effect_time(men_old_pooled_two_effect_gamma_log, men_old_pooled_one_gamma_log, 0.08)
sim_two_effect_time(men_pooled_two_effect_gamma_log, men_pooled_one_gamma_log, 0.08)
```

@@

This runs the sim_two_effect_prob function at a probability of 1 in every 1,000
sprinters.
```{r}
#9
sim_two_effect_prob(men_old_finals_two_effect_gamma_log, men_old_finals_one_gamma_log, 0.001)
sim_two_effect_prob(men_finals_two_effect_gamma_log, men_finals_one_gamma_log, 0.001)
sim_two_effect_prob(men_old_pooled_two_effect_gamma_log, men_old_pooled_one_gamma_log, 0.001)
sim_two_effect_prob(men_pooled_two_effect_gamma_log, men_pooled_one_gamma_log, 0.001)
```

The code below repeats the previous section but for an average of 1 in every
10,000 sprinters.
```{r}
#10
sim_two_effect_prob(men_old_finals_two_effect_gamma_log, men_old_finals_one_gamma_log, 0.0001)
sim_two_effect_prob(men_finals_two_effect_gamma_log, men_finals_one_gamma_log, 0.0001)
sim_two_effect_prob(men_old_pooled_two_effect_gamma_log, men_old_pooled_one_gamma_log, 0.0001)
sim_two_effect_prob(men_pooled_two_effect_gamma_log, men_pooled_one_gamma_log, 0.0001)
```

>>>>

---
title: "GLMM"
author: "Owen Fiore"
date: "2023-05-31"
output: pdf_document
---

@@

The code below loads in the 4 datasets from the csv file.
```{r}
#1
times <- read.csv("../Data/Thesis2023.csv")
colnames(times) <- c("Year", "Type", "Time", "RxnTime", "Gender", "Batch")
men_finals <- subset(times, Type == "F" & Gender == "M" & Time != 'DQ')
men_pooled <- subset(times, (Type == "F" | Type == "S") & 
                       Gender == "M" & Time != 'DQ')
men_old_finals <- subset(times, Type == "F" & Gender == "M" & 
                           Time != 'DQ' & Year != 2022)
men_old_pooled <- subset(times, (Type == "F" | Type == "S") & 
                           Gender == "M" & Time != 'DQ' & Year != 2022)
```

@@

```{r}
summary(men_pooled_year_gamma_log)
summary(men_old_pooled_year_gamma_log)
```

@@

```{r}
summary(men_pooled_batch_gamma_log)
```

This creates the models with a year effect and batch effect.
```{r}
#5
library(lme4)
men_old_finals_two_effect_gamma_log <- glmer(RxnTime ~ (1 | Year) + (1 | Batch), 
                                   data = men_old_finals, family = Gamma(link = "log"))
men_finals_two_effect_gamma_log<- glmer(RxnTime ~ (1 | Year) + (1 | Batch), 
                              data = men_finals, family = Gamma(link = "log"))
men_old_pooled_two_effect_gamma_log <- glmer(RxnTime ~ (1 | Year) + (1 | Batch), 
                                   data = men_old_pooled, family = Gamma(link = "log"))
men_pooled_two_effect_gamma_log <- glmer(RxnTime ~ (1 | Year) + (1 | Batch), 
                               data = men_pooled, family = Gamma(link = "log"))
```
```{r}
summary(men_pooled_two_effect_gamma_log)
summary(men_old_pooled_two_effect_gamma_log)
```

@@

This next chunk of code runs the simulation code for each dataset comparing the
two effect model to the base model
```{r}
#7
set.seed(1)
sim_two_effect_time(men_old_pooled_two_effect_gamma_log, men_old_pooled_one_gamma_log, 0.1)
sim_two_effect_time(men_pooled_two_effect_gamma_log, men_pooled_one_gamma_log, 0.1)
```

```{r}
set.seed(1)
sim_two_effect_time(men_old_pooled_two_effect_gamma_log, men_old_pooled_one_gamma_log, 0.09)
sim_two_effect_time(men_pooled_two_effect_gamma_log, men_pooled_one_gamma_log, 0.09)
```

```{r}
set.seed(1)
sim_two_effect_time(men_old_pooled_two_effect_gamma_log, men_old_pooled_one_gamma_log, 0.08)
sim_two_effect_time(men_pooled_two_effect_gamma_log, men_pooled_one_gamma_log, 0.08)
```

@@

This runs the sim_two_effect_prob function at a probability of 1 in every 1,000
sprinters.
```{r}
#9
set.seed(1)
sim_two_effect_prob(men_old_pooled_two_effect_gamma_log, men_old_pooled_one_gamma_log, 0.001)
sim_two_effect_prob(men_pooled_two_effect_gamma_log, men_pooled_one_gamma_log, 0.001)
```

The code below repeats the previous section but for an average of 1 in every
10,000 sprinters.
```{r}
#10
set.seed(1)
sim_two_effect_prob(men_old_pooled_two_effect_gamma_log, men_old_pooled_one_gamma_log, 0.0001)
sim_two_effect_prob(men_pooled_two_effect_gamma_log, men_pooled_one_gamma_log, 0.0001)
```
